Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection

### 2019-06-05 reports/paper1/paper.tex
Intro rewritten

\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
\date{2019}
\author{
  Sherman Lo \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams \and Jason Warnett
}

@@

Quality control in additive manufacturing can be done using x-ray computed tomography (CT) \citep{thompson2016x}. The CT is compared with the computer-aided design (CAD) so that voids and surface deviation can be measured in terms of position and size \citep{villarraga2015assessing, lee2015compliance, kim2016inspection}. The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample. Speeding up the quality control process on the production line could be done by doing an inspection using a fewer number of projections by sacrificing accuracy \citep{warnett2016towards, brierley2018optimized}.

A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. Beforehand, however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

An x-ray projection of a 3D printed sample was obtained and compared with the simulation in an experiment. The procedure is shown in the methods section along with the description of the empirical null filter. In addition, the software development and simulation studies of the filter were discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

Two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} was used to quantify the disagreement of each pixel between the projection and the simulated projection. A disagreement too big will classify that pixel as a positive result. A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.

@@

The empirical null filter catered for inaccuracies made by \emph{aRTist} and voids in the order of millimetres were detectable. This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference. In the experiments, it was found that the FDR level is preserved after filtering.

>>>>

\title{Local normalisation using the empirical null for inspection of additive manufacturing using a single x-ray projection}
\date{2019}
\author{
  Sherman Lo \and Jason Warnett \and Gregory Gibbons \and Thomas Nichols \and Julia Brettschneider \and Mark Williams
}

@@

Additive manufacturing (AM) is capable of manufacturing objects with complicated internal and external geometries. One example of AM technology is fused deposition modelling (FDM) \citep{crump1991fused, crump1992apparatus, stratasys2019what}. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer.

However, there is a need for product inspection and in particular assessing the quality of the internal structures. For example, voids can form between layers which can hinder the mechanical properties of the product \citep{wang20173d, ngo2018additive}. In power based AM technologies, gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}. Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}.

Non-destructive testing can be used to assess the quality of the product such as x-ray computed tomography (XCT). The object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam \citep{kruth2011computed}. The x-ray projections are then used to reconstruct the object in 3D \citep{brooks1976principles, feldkamp1984practical, smith1990cone}.

XCT is commonly used for the investigation of pores in the manufactured object \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}. The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.

The strength of XCT comes from the fact that the location of the pores can be visualised. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}. \cite{leuders2015fatigue} pointed out that the location of the pores is an important factor. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \linebreak\citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

The disadvantage of x-ray CT is that it involves the acquisition and reconstruction of thousands of projections of the sample. Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}.

Instead of reconstructing the object, the analysis can be done on a single x-ray projection itself by comparing it to a simulated projection such as \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \cite{brierley2018optimized} demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without. It is however inevitable that accuracy is lost from the jump from 3D to 2D \citep{hayden2009chest}.

It was investigated whenever defects can be detected from a single x-ray projection. This was done by obtaining an x-ray projection of a 3D printed sample, with purposely designed voids, and comparing it with the simulation. The apparatus and procedures are shown in the methods section. In addition, software development and simulation studies were discussed. The results from the simulation and the experiment are shown in the results section. The conclusion section summarises the study along with a discussion on further work.

@@

A method was proposed to compare a single projection with a simulation of that projection and treating it as the ground truth. This was done by using two-tailed multiple hypothesis testing \citep{pearson1900on, neyman1933on, fisher1970statistical} controlling the false discovery rate (FDR) \citep{benjamini1995controlling, benjamini2010discovering}, treating each pixel as an individual test. A disagreement too big will classify that pixel as a positive result. Beforehand, however, the empirical null \citep{efron2004large} was used to do local normalisation on the test statistics. This was necessary because the simulation of the projection did not perfectly reproduce the obtained projection, leading to incorrect inference.

A test statistic $Z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This test statistic, together makes a $z$ image, is
\begin{equation}
  Z_{x,y} = 
  \dfrac{
    \text{projection}_{x,y} - \emph{aRTist}_{x,y}
  }
  {
    \sqrt{\widehat{\variance}\left[\text{projection}_{x,y}\right]}
  }
\end{equation}
where $\widehat{\variance}\left[\text{projection}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the projection.

@@

Voids in the order of millimetres were detectable which shows potential in defect detection in projection space. This can be extended to multiple projections and perhaps in real time on a conveyor belt.

The empirical null filter catered for inaccuracies made by \emph{aRTist}. This demonstrated that the filter can adjust the null hypotheses according to the data to make sensible inference. In the experiments, it was found that the FDR level is preserved after filtering.
